Designing a Search for the BBC

### 2014-02-12 paper.tex
Added changes as given by Huseyin.

\begin{abstract}
This paper combines Soft Systems Methodology and UML modelling to design a
high-level view of a search application that receives web content
from a variety of BBC content production systems and makes every item
then searchable by a BBC website visitor using the search feature.
\end{abstract}

@@

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in Fig.~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive a search-based discovery of
those websites.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around users seeking educational
and informative material such as GCSE Bitesize or any other
learning resouces.

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonsrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illutration for such a message-based integration
system might be derived from the illutrated patterns created
by Hohpe and Woolf. \citep{hohpe2004enterprise}

@@

The latter pattern fully decouples the search indexes from any
deeper information -- leaving that responsbility to appropriate
source system -- but means that the raw, stub results are near-useless
to an end user. This makes the AJAX-based alternative approach
in Fig.~\ref{sequence-ajax}
less of a desirable option (would a user really be presented a list
of URIs while some Javascript code replaces them one by one with
actual information?). Given the AJAX-driven behaviour still appears
desirable in terms of responsiveness, it would seem that some trade-off
would need to happen in terms of what the indexes store as additional
information.

These decisions relate to how the system would implement the data model
in Fig.~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
\citep{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

@@

\appendix
\section{Proposal}

\input{proposal-contents}

>>>>

\begin{abstract}

Whilst there are successful general web search engines such a Google that
will find any piece of content, there is a perceived need for a specific
search that makes better use of the internal knowledge the broadcasting
industry (e.g. BBC) has about its own content. The British Broadcasting
Corporation (BBC) is a public service broadcaster funded by the licence
fee paid by United Kingdom households. This industry-based case study
combines Soft Systems Methodology (SSM) and Unified Modelling Language
(UML) to design a high-level view of a search application that receives
web content from a variety of BBC content production systems and makes
every item then searchable by a BBC website visitor using the search
feature. The developers of such search applications can benefit from this
specific industry-based case study that contextualised the problem space
using SSM and developed UML models to solve the problem.

\end{abstract}

@@

Dogan and Henshaw\citep{dogan2010conceptual}
showed how a ‘soft’ systems approach called Interactive
Management can be adopted to capture the requirements and contextualise the
problem space. This involved the process of transitioning from the soft systems
results to a formal model (e.g. UML). This transition was enabled by dividing
the actors in the rich pictures into meta-level and direct users of the system.
Although this division was subjective and depended on the interpretation  and
analysis of the rich pictures to provide a structure for the use case model,
the rich pictures themselves were created through interactions with subject
matter experts. The soft systems, and hence the Interactive Management results,
provided the baseline information to derive a formal model including UML use
case, sequence and domain models. The transitioning from ``soft'' to ``hard''
systems can be set within the State of the Art including the requirements
analysis and modelling as used in SSM, UML and Business Process Modelling.

The overall design objective of this paper will be to create an initial
proposal for a
search application to drive the missing components within the holistic
system depicted in Fig.~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive a search-based discovery of
those websites.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around users seeking educational
and informative material such as GCSE Bitesize or any other
learning resources.

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonstrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illustration for such a message-based integration
system might be derived from the illustrated patterns created
by Hohpe and Woolf. \citep{hohpe2004enterprise}

@@

The latter pattern fully decouples the search indexes from any
deeper information -- leaving that responsibility to appropriate
source system -- but means that the raw, stub results are near-useless
to an end user. This makes the AJAX-based alternative approach
in Fig.~\ref{sequence-ajax}
less of a desirable option (would a user really be presented a list
of URIs while some Javascript code replaces them one by one with
actual information?). Given the AJAX-driven behaviour still appears
desirable in terms of responsiveness, it would seem that some trade-off
would need to happen in terms of what the indexes store as additional
information.

These decisions relate to how the system would implement the data model
in Fig.~\ref{model}. The ontology described is an aggregation
of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
\citep{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

@@

A post-analysis study is required to evaluate the SSM and UML models. The models
need to be applied to further projects for validation and verification purposes.
In addition, the maturity and evolution of the artefacts need to be considered
e.g. adding, deleting, or modifying, if the boundary and context changes.
